---
title: "Administering the Database"
author: "Matt Espe"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Telemetry API Administration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, setup, include = FALSE}
library(telemetry)
```

# Creating New Entries

New entries (users, affiliations, organizations) are done via the
`create_entry()` function. This function is built to be flexible
around any of the `/api/admin/create/*` end-points. The general use of
the `create_entry()` function is to provide a session for an existing
user, and then list the required variables for the entry using `key =
value` entries separated by commas. The key must match the appropriate
required keys for each end-point.

The available endpoints can be listed with

```{r}
list_endpoints()
```

As each end-point has different required keys that can be difficult to
remember and keep straight, there is a convienence function to list
the required variables for a particular end-point. For example, to
list the required variables for the `/api/admin/create/user` endpoint

```{r}
list_endpoint_variable("/api/admin/create/user")
```

Note that the end-point must match to one of those listed by the
`list_endpoints()` function.

## Creating Users

Creating a new user must be done from an existing user with adequate
permissions.

To create a new user, we must provide `createUserInfo`, `unUserName`,
`createUserPass`, and the `unToken` for an already authorized user.

```{r, eval = FALSE}

create_entry(my_session,
             createUserInfo = "nothing here",
             unUserName = "Matt",
             createUserPass = "qwerty",
             unToken = my_session$unToken,
             end_point = "/api/admin/create/user")
```

This will create a new user named "Matt" in the database. However,
this new user is not affiliated with any organization and hence will
not have access to any data. 

We need to either affiliate this new user with an existing
organization, or we need to create a new organization and then
affiliate the new user with the new organization.

Here, we will just add this user to an existing organization.

First, we'll list the current organizations,

```{r, eval = FALSE}
list_db_entry("orgs", session = a)
```
```
  orgID orgName                           orgInfo
1     1    PITA                PIT Administration
2     2    NATO North Atlantic Trout Organization
```

We would like to add "Matt" to the organization 2. We can do that with
another call to `create_entry()`, but now with the correct variables
for the `/api/admin/create/affiliation` endpoint.

```{r, eval = FALSE}
create_entry(my_session, unOID = 2, unUID = 3, unToken = my_session$unToken,
             end_point = "/api/admin/create/affiliation")
```

This adds "Matt" as a user affiliated with the "NATO" organization. We
can check this by listing the users associated with organization 2
using the `list_db_entry()` function

```{r, eval = FALSE} 
list_db_entry("users", 2, my_session)

```

```
  userDataID userDataName                                  userDataInfo
1          2         Alex this user did not provide contact information
2          3         Matt                                  nothing here
```

