---
title: "Administering the Database"
author: "Matt Espe"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Telemetry API Administration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, setup, include = FALSE}
library(telemetry)
```

# Overview of the `send_api_request()` function

Most interactions with the database are performed via the
`send_api_request()` function. This function helps the R user create
valid API requests and submits them to the API. Since most
interactions will happen via this function, it is worth understanding
how this functions works.

First, the `send_api_request()` function is a flexible function for
submitting *most* API requests via a single interface. In order to
achieve this flexibility, the function takes an active session object
created via `start_session()`, an endpoint to submit the request to
(one of the options as listed by `list_endpoints()`), and then a set of
`key = value` pairs required by the endpoint specified as additional
arguments to the function (see case study below for example).

The required `key = value` pairs are different for each endpoint, yet
the mechanism for submitting them is similar in any case. For
example, if the endpoint requires the variable "unTagName", this
can be provided to `send_api_request()` like
	
```{r, eval = FALSE}
send_api_request(session = my_session,
                 unTagName = "some_tag_name",
                 end_point = "/api/some/endpoint")
```


There are two important details to remember about the keys: 1) the key
must match the appropriate required keys for each end-point exactly
(keys are case-sensitive), and 2) all keys for a given endpoint must
be supplied.

As each end-point has different required keys that can be difficult to
remember and keep straight, there is a convenience function to list
the required variables for a particular end-point. For example, to
list the required variables for the `/api/admin/create/user` endpoint

```{r}
list_endpoint_variable("/api/admin/create/user")
```

## Case Study: Creating New User Entry

Creating a new entries for users is done via the `send_api_request()`
function. The general use of the `send_api_request()` function is to
provide a session for an existing user, and then list the required
variables for the entry using `key = value` entries separated by
commas.

### Finding required variables to include

First, we will check the required keys for the `/api/admin/create/user` endpoint

```{r}
list_endpoint_variable("/api/admin/create/user")
```

This shows that we need to provide 4 values for this request;
"createUserInfo", "unUserName", "createUserPass", and "unToken".

### Creating a New User

*NOTE: Creating a new user must be done from an existing user with
adequate permissions. Thus, the "unToken" provided is for an existing
session for an existing user.*

To create a new user, we must provide `createUserInfo`, `unUserName`,
`createUserPass`, and the `unToken` for an already authorized user's
login session (i.e. a session object created via `start_session()`)..

```{r, eval = FALSE}

send_api_request(my_session,
                 createUserInfo = "nothing here",
                 unUserName = "Matt",
                 createUserPass = "qwerty",
                 unToken = my_session$unToken,
                 end_point = "/api/admin/create/user")
```

This will create a new user named "Matt" in the database. However,
this new user is not affiliated with any organization and hence will
only have access to data that is not registered to an organization. 

### Adding a New User to an Organization

We need to either affiliate this new user with an existing
organization, or we need to create a new organization and then
affiliate the new user with the new organization.

Here, we will just add this user to an existing organization.

First, we'll list the current organizations,

```{r, eval = FALSE}
send_api_request(session = a,
                 end_point = "/api/list/orgs",
                 unToken = a$unToken)
```
```
  orgID orgName                           orgInfo
1     1    PITA                PIT Administration
2     2    NATO North Atlantic Trout Organization
```

We would like to add "Matt" to the organization 2. We can do that with
another call to `send_api_request()`, but now with the correct variables
for the `/api/admin/create/affiliation` endpoint ("unOID", "unUID", and "unToken").

```{r, eval = FALSE}
send_api_request(my_session,
                 unOID = 2,
                 unUID = 3,
                 unToken = my_session$unToken,
                 end_point = "/api/admin/create/affiliation")
```

This adds "Matt" as a user affiliated with the "NATO" organization. We
can check this by listing the users associated with organization 2
using the `list_db_entry()` function

```{r, eval = FALSE} 
list_db_entry("users", 2, my_session)
```

```
  userDataID userDataName                                  userDataInfo
1          2         Alex this user did not provide contact information
2          3         Matt                                  nothing here
```

## Registration Data Upload

There are a few particularities to be aware of when uploading new
registration data to the database.

First, the registrations must be for an antenna already entered into
the database (i.e. one that is listed by
`list_db_entry("antenna")`). If the antenna is not already
in the database, it must be added prior to uploading the registration
data. 

Second, the registrations should be organized into a `data.frame` with
columns named "unAntName" (the unique antenna name), "unTagName" (the
unique tag name), and "regDataTime" (a POSIX timestamp for the
registration, including the timezone). Additional columns can be
appended to the data via the `data_cols` argument - a vector of the
column names of additional columns to be included in the "payload"
slot of the registrations table. These additional columns will be
marshalled to JSON before being stored in the "payload" slot.

Once the registrations have been prepared according to the above
requirements, it can be uploaded to the database with
`api_upload_data()`. As with all the other API functions, it requires
an active session.

```{r, eval = FALSE}
api_upload_data(session = my_session,
                registration_data = new_registration_df,
                other_data_column_names = c("temperature", "turbidity"))
                
```

It is worth noting that any tag names can be included in the
registrations, including ones not listed in the "Tags" table. On upload, if
another organization has claimed ownership of a tag ID, the new
registration data associated with that tag will automatically become
associated with that organization.

**Q: Is this weird? This means the uploading organization might not be
able to see the data they just uploaded.**

**Q: Is there any way to resolve tag collisions? (two distinct tags with the same tag name)**



