---
title: "Quickstart Guide for the Telemetry API"
author: "Matt Espe"
date: "2024 Mar 19"

---

## Establishing a Session

In order to start interacting with the API server, you must first
establish a session using a pre-established set of login credentials
(Username and Password). It is best practice to avoid storing these in
files which are easily shared with others either directly or
indirectly (e.g. an accidental git commit). Please note, this includes
.Rhistory files (which store console commands). Therefore, you want to
use the password in a way that defines it without ever printing it in
your script or R console.

A simple way to enact this is to stored login credentials in a file
that is separate from the analysis script, and is ignored by git in a
.gitignore file:

```{r}
## Defines api_url, usr, and pwd
source("api_credentials.R", echo = FALSE)
```

Using these, we can establish a session,

```{r}
library(telemetry)
my_session = start_session(usr, pwd, api_url)
```

The returned object stores all the information about the session that
was just established, including the user who started the session, the
time the session was started (as the session will timeout after some
time), a curl handle for the session, and a unique token for the
server to identify the session.

